### 2022-05-31 article.tex
Add examples, improve table

There are multiple websites for hosting code, with BitBucket, GitHub,
GitLab and SourceForge being the most well-known.
Of these, GitHub is the most popular website to host code in general,
with millions of users.
GitHub users can create dedicated websites (called 'repositories')
to upload code. GitHub hosts that uploaded by and provides
a user interface for every visiter of such a website.
The use of code hosting websites, such as GitHub,
accommodates collaboration (\cite{perez2016ten}).
\begin{sloppypar}\url{https://github.com/richelbilderbeek/babette},\end{sloppypar}
and improves transparency (\cite{gorgolewski2016practical}).
An example from the author is the website \cite{bbbqarticleissue157},
that hosts part of the code for the paper \cite{bilderbeek2022transmembrane}.

@@

Most code hosts, among others, GitHub and GitLab,
automatically keep track of certain metrics.
One such metric is the amount of code each contributor has made.
In that way, authors involved in the writing of the software
are honestly acknowledged.

@@

>>>>

There are multiple websites for hosting code, with BitBucket, GitHub,
GitLab and SourceForge being the most well-known.
Of these, GitHub is the most popular website to host code in general,
with millions of users.
GitHub users can create dedicated websites (called 'repositories')
to upload code. GitHub hosts that uploaded by and provides
a user interface for every visiter of such a website.
The use of code hosting websites, such as GitHub,
accommodates collaboration (\cite{perez2016ten}).
\begin{sloppypar}\url{https://github.com/richelbilderbeek/babette},\end{sloppypar}
and improves transparency (\cite{gorgolewski2016practical}).
An example from the author is the website \cite{bbbqarticleissue157},
that hosts part of the code for the paper \cite{bilderbeek2022transmembrane},
as shown in Figure \ref{fig:bbbqarticleissue157}.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{bbbq_article_issue_157.png}
  \caption{
    A typical GitHub repository (\cite{bbbqarticleissue157}), 
    hosting the code for a
    computational experiment, 
    as published with \cite{bilderbeek2022transmembrane}.
    Note that this repository has 72 commits, where a commit is a change
    to the code.
  }
  \label{fig:bbbqarticleissue157}
\end{figure}

@@

Most code hosts, among others, GitHub and GitLab,
automatically keep track of certain metrics.
One such metric is the amount of code each contributor has made.
In that way, authors involved in the writing of the software
are honestly acknowledged. Figure \ref{fig:daisie_contributors}
shows the number of commits the authors of DAISIE (\cite{etienne2020daisie})
have made to its code.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{daisie_contributors.png}
  \caption{
    An overview of the commits that multiple contributors have
    made, in this case, to the code of DAISIE (\cite{etienne2020daisie})
  }
  \label{fig:daisie_contributors}
\end{figure}

@@

\begin{table}[h]
  \begin{tabular}{|l|p{9cm}|}
    \hline
    \textbf{Type of code} & \textbf{Recommendation} \\
    \hline
    No code       & Disallow papers that do not supply code publicly \\
    \hline
    Raw code      & Don't publish raw code as text, instead, host it on a code hosting website \\
    \hline
    Hosted code   & Add CI. Use standarized badges for build status and code coverage. 
                    Provide for a standarized way to link between paper and code host \\
    \hline
    Runnable code & Provide website to upload containers with proper annotation.
                    Provide for a standarized way to link between container, paper and code repository \\
    \hline
  \end{tabular}
  \caption{Recommendations described in this paper}
  \label{tab:recommendations}
\end{table}
